--- 
title: "R na Cozinha"
author: "Paulo Guilherme Pinheiro dos Santos"
date: "`r format(Sys.Date(), '%d de %B de %Y')`"
site: bookdown::bookdown_site
documentclass: book
bibliography: [book.bib, packages.bib]
biblio-style: apalike
link-citations: yes
description: "Este é a minha contribuição ao ensino do R. Foi elaborado graças ao pacote `bookdown`."
url: 'https\://pgpinheiro2.github.io/R_pg2_book/'
lang: pt-br
---

# Apresentação

This is a _sample_ book written in **Markdown**. You can use anything that Pandoc's Markdown supports, e.g., a math equation $a^2 + b^2 = c^2$.

The **bookdown** package can be installed from CRAN or Github:

```{r echo=F, eval=FALSE}
install.packages("bookdown")
# or the development version
# devtools::install_github("rstudio/bookdown")
```

Remember each Rmd file contains one and only one chapter, and a chapter is defined by the first-level heading `#`.

To compile this example to PDF, you need XeLaTeX. You are recommended to install TinyTeX (which includes XeLaTeX): <https://yihui.org/tinytex/>.

```{r include=FALSE}
# automatically create a .bib database for R packages; salva os detalhes no arquivo "packages.bib"
knitr::write_bib(
  c(.packages(), 'bookdown', 'knitr', 'rmarkdown'),
  'packages.bib'
  )
```
